shrimp_goby_boatnoise

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
removing redundant text
updating the directory structure

This is a test from the cooding god

@@

##1.2 Unblinding the data
```{r}
#assigning the directory so that the code can be universally read on any computer as long as the entire project file is shared
directory <- './1-data/'

#reading in the coded raw BORIS output
BORIS_output <- read.csv("./1-data/BORIS_output_update.csv")

#reading in the decoder
Video_codes <- read.csv("./1-data/Video_codes.csv")

shrimp_species <- read.csv("./1-data/species.csv")

>>>>

@@

##1.2 Unblinding the data
```{r}
#assigning the directory so that the code can be universally read on any computer as long as the entire project file is shared
directory <- './2-data/'

#reading in the coded raw BORIS output
BORIS_output <- read.csv("./2-data/BORIS_output_update.csv")

#reading in the decoder
Video_codes <- read.csv("./2-data/Video_codes.csv")

shrimp_species <- read.csv("./2-data/species.csv")
